---
title: "Clust_01"
author: "Ricardo Herena"
date: "8/5/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Documents/Text Analysis Pred 453/P454_TextCluster")
library("tm")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library(cluster)
```


```{r read_data}

c_m = read.csv("dtms.csv", sep=",", row.names=1)
dsi_m <- t(c_m)
d_m <- dist(c_m, method="euclidean")
dsi_m <- dist(dsi_m, method="euclidean")

```

Below are some word clouds. We can use these to understand our matrix from a high level. We can also compute tf-idf for word clouds. 

```{r tf-idf-wordclouds}

#tf-idf totals for plotting
v <- sort(rowSums(c_m),decreasing=TRUE)
d <- data.frame(word = names(v),freq=v)

set.seed(1234)
wordcloud(words = d$word, freq = d$freq, min.freq = 1,
          max.words=200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))


```

Hierarchical Clustering

We can see various clusters emerging from our Hclust. We write this to a PDF. A we can see there are many clusters that stem from the top. Our initial guess is something like 10-20 clusters, but very messy ones for the word concepts, and around 6 DSI clusters as identified by prior cohorts.

```{r hclust1}

hcl <- hclust(d_m)
plot(hcl)

pdf("hcl.pdf", width=40, height=15)
plot(hcl)
dev.off()


hcl2 <- hclust(dsi_m)
plot(hcl2)

pdf("hcl2.pdf", width=40, height=15)
plot(hcl2)
dev.off()

```

Given that we are most interested in clustering DSI's, we can see roughly 10 clusters for DSI's. Below we present tables for how many DSI's end up in clusters for clusters 10:15. It seems there are diminishing returns for more than 12 clusters in terms of being well distributed. 


```{r hclust2}

## DSI clusters sums


rowSums(table(cutree(hcl2, 10),colnames(c_m)))

rowSums(table(cutree(hcl2, 11),colnames(c_m)))

rowSums(table(cutree(hcl2, 12),colnames(c_m)))

rowSums(table(cutree(hcl2, 13),colnames(c_m)))

rowSums(table(cutree(hcl2, 14),colnames(c_m)))

rowSums(table(cutree(hcl2, 15),colnames(c_m)))


### DSI clusters
write.csv(table(cutree(hcl2, 3),colnames(c_m)),
          paste("H_clustDSI_firstpass", ".csv", sep = ""))



```


```{r keywords}

## Keyword concept clusters 
nclust <- 10

t <- table(d$word, cutree(hcl, nclust))
t2 <- table(d$word, cutree(hcl, nclust + 10))
t3 <- table(d$word, cutree(hcl, nclust + 20))

colSums(t, 1:nclust)

colSums(t2, 1:nclust+10)

colSums(t3, 1:nclust+20)


write.csv(t2,
          paste("H_TERMS_firstpass", ".csv", sep = ""))


```






